---
title: "covariates"
author: "hoskisson"
date: "2023-03-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rtweet)
library(tidyverse)
```

## Compile a table with list of Senators in the 117th congress
Sources:
https://www.congress.gov/members?q=%7B%22congress%22%3A117%2C%22chamber%22%3A%22Senate%22%7D
https://github.com/unitedstates/congress-legislators
```{r}
legislators_current <- read.csv("data/legislators-current.csv") %>%
  filter(type == "sen")
legislators_current$last_name <- tolower(legislators_current$last_name)
legislators_current$first_name <- tolower(legislators_current$first_name)


legislators_historical <- read.csv("data/legislators-historical.csv") %>%
  filter(type == "sen")

legislators_historical$last_name <- tolower(legislators_historical$last_name)
legislators_historical$first_name <- tolower(legislators_historical$first_name)
# data I compiled by hand of the 117th congress
# omitted Kamala Harris and Kelly Loeffler because they were not in chamber
# at time of votes on bills I'm interested in
senator_data <- read.csv("data/senator_data.csv")
```

Join current legislators data
```{r}
# join with current legislators list
senator_data_a <- senator_data %>%
  left_join(legislators_current, by = c("last_name", "first_name")) %>%
  select(c(id:first_name, middle_name, full_name, birthday, gender.y, state.y, type, party.y, govtrack_id, ballotpedia_id))

# clean joined data
senator_data_a <- senator_data_a %>%
  mutate(
    party = party.y,
    gender = gender.y,
    state = state.y
  ) %>%
  select(-party.y, -gender.y, -state.y) %>%
  filter(!is.na(party)) # only keep the ones we have data for--use party column to indicate this
```

Join historical legislator data
```{r}
senator_data_b <- senator_data %>%
  left_join(legislators_historical, by = c("last_name", "first_name")) %>%
  select(c(id:first_name, middle_name, full_name, birthday, gender.y, state.y, type, party.y, govtrack_id, ballotpedia_id))

# clean joined data
senator_data_b <- senator_data_b %>%
  mutate(
    party = party.y,
    gender = gender.y,
    state = state.y
  ) %>%
  select(-party.y, -gender.y, -state.y) %>%
  filter(!is.na(party)) # only keep the ones we have data for--use party column to indicate this

# remove JFK because it is a false match
senator_data_b <- senator_data_b %>%
  filter(last_name != "kennedy")
```

Join current and historical together
```{r}
senator_data_c <- full_join(senator_data_a, senator_data_b) %>%
  arrange(id)
```

record senator_data_c
```{r}
write.csv(senator_data_c,"data/senator_data_c.csv")
```

## Add race and ethnicity

Read in race and ethnicity datasets

*Sources for these:*
Export list of members by biographical characteristics. Washington: CQ Press. Dynamically generated March 31, 2023, from CQ Press Electronic Library, CQ Press Congress Collection: https://library.cqpress.com/congress/export.php?which=memberbioadv&congress2=236&position2=2&yearlimit=0&race=1
Export list of members by biographical characteristics. Washington: CQ Press. Dynamically generated March 31, 2023, from CQ Press Electronic Library, CQ Press Congress Collection: https://library.cqpress.com/congress/export.php?which=memberbioadv&congress2=236&position2=2&yearlimit=0&race=4
Export list of members by biographical characteristics. Washington: CQ Press. Dynamically generated March 31, 2023, from CQ Press Electronic Library, CQ Press Congress Collection: https://library.cqpress.com/congress/export.php?which=memberbioadv&congress2=236&position2=2&yearlimit=0&race=6
Export list of members by biographical characteristics. Washington: CQ Press. Dynamically generated March 31, 2023, from CQ Press Electronic Library, CQ Press Congress Collection: https://library.cqpress.com/congress/export.php?which=memberbioadv&congress2=236&position2=2&yearlimit=0&race=3
Export list of members by biographical characteristics. Washington: CQ Press. Dynamically generated March 31, 2023, from CQ Press Electronic Library, CQ Press Congress Collection: https://library.cqpress.com/congress/export.php?which=memberbioadv&congress2=236&position2=2&yearlimit=0&race=2

Some of the first names have been manually altered to match my previous data. For example, Addison Mitch McConnell was 
changed to Mitch McConnel to match what was in my senator dataset even though Addison Mitch McConnell is probably
the correct name.

Alejandro (Alex) Padilla is latino per: https://history.house.gov/People/Search?Term=Search&SearchIn=LastName&ShowNonMember=true&ShowNonMember=false&Office=&Leadership=&State=&Party=&ContinentalCongress=false&BlackAmericansInCongress=false&WomenInCongress=false&HispanicAmericansInCongress=true&HispanicAmericansInCongress=false&AsianPacificAmericansInCongress=false&CongressNumberList=117&PreviousSearch=Search%2cLastName%2c%2c%2c%2c%2cFalse%2cFalse%2cFalse%2c117%2cLastName&CurrentPage=4&SortOrder=LastName&ResultType=Grid&Command=3

Added Raphel Warnock to African American list per:
https://history.house.gov/People/Search?Term=Search&SearchIn=LastName&ShowNonMember=true&ShowNonMember=false&Office=&Leadership=&State=&Party=&ContinentalCongress=false&BlackAmericansInCongress=true&BlackAmericansInCongress=false&WomenInCongress=false&HispanicAmericansInCongress=false&AsianPacificAmericansInCongress=false&CongressNumberList=117&PreviousSearch=Search%2cLastName%2c%2c%2c%2c%2cFalse%2cTrue%2cFalse%2c117%2cLastName&CurrentPage=1&SortOrder=LastName&ResultType=Grid&Command=6

```{r}
hispanic_senators <- read.csv("data/race_ethnicity/hispanic_117_senate.csv")
race_not_specified_senators <- read.csv("data/race_ethnicity/race_not_specified_117_senate.csv")
white_senators <- read.csv("data/race_ethnicity/white_117_senate.csv")
african_american_senators <- read.csv("data/race_ethnicity/african_american_117_senate.csv")
asian_american_senators <- read.csv("data/race_ethnicity/asian_american_117_senate.csv")
```
```{r}
hispanic_senators <- data.frame(lapply(hispanic_senators, tolower))
race_not_specified_senators <- data.frame(lapply(race_not_specified_senators, tolower))
white_senators <- data.frame(lapply(white_senators, tolower))
african_american_senators <- data.frame(lapply(african_american_senators, tolower))
asian_american_senators <- data.frame(lapply(asian_american_senators, tolower))
```




Add the race data to senator data
```{r}
race_data_senators <- rbind(hispanic_senators, race_not_specified_senators, white_senators, african_american_senators, asian_american_senators)

senator_data_d <- senator_data_c %>%
  left_join(select(race_data_senators, Race, Last, First), by = c("last_name" = "Last", "first_name" = "First"))
```

## Create list of senator handles

```{r}
members <- lists_members(list_id = 63915645 )
senator_handles_list <- members$screen_name
senator_handles_df<-as.data.frame(senator_handles_list)
write.csv(senator_handles_df$senator_handles_list, "data/senator_handles_from_twitter_list.csv")
```

```{r}
# loop through list of senators
senator_data_match <- senator_data_d
senator_data_match$num_matches <- 0
senator_handles_df<-as.data.frame(senator_handles_list)
senator_handles_df$last_name <- NA
senator_handles_df$senator_id <- NA
senator_handles_df <- data.frame(lapply(senator_handles_df, tolower))


for(i in 1:nrow(senator_data_match)){
  last_name <- senator_data_match[i,]$last_name
  senator_id <- senator_data_match[i,]$id
  # if last name has hyphen or space, split and take first part
  last_name <- unlist(strsplit(last_name, "-|\\s"))[1]
  match_indx <- grep(last_name, senator_handles_df$senator_handles_list)
  if(length(match_indx) == 0) {
    # go to next senator in list if no match
    # don't attempt to record name or increment num_matches
    next
  }
  num_match <- length(match_indx)
  senator_handles_df[match_indx,]$last_name <- last_name
  senator_handles_df[match_indx,]$senator_id <- senator_id
  senator_data_match[i,]$num_matches <- senator_data_match[i,]$num_matches + num_match
}

write.csv(senator_handles_df, "data/senator_handles_table_draft.csv", row.names = FALSE)
write.csv(senator_data_match, "data/senator_data_match.csv", row.names = FALSE)
```

Record senator_data_d for later use
```{r}
write.csv(senator_data_d, "data/senator_data_d.csv", row.names = FALSE)
```


I manually checked the `senator_handles_table_draft.csv` file to make sure that the matches from
`senator_data_match` were the correct ones. There were a few corrections, including:
- Hyde-Smith and Smith
- the two Scotts
- Ben Lujan, manually matched

Now working on those who came up with 0 matches in the `senator_data_match`
And those who have `NA` in the `senator_handles_table.csv` file.

These handles belong to Senators who were not part of the Senate in the timeframes in question,
they have been removed manually from `senator_handles_table.csv`. Identified by seeing `NA`
in `senator_handles_table.csv`
- Kamala Harris (142)
- SenAlexander, Lamar Alexander (128)
- lamaralexander, Lamar Alexander (155)

Senator handles added which were identified by spotting a 0 in the `senator_data_match.csv` file.
- benraylujan maunually matched to Ben Lujan
- senatorlujan manually matched to Ben Lujan
- AlexPadilla4CA
- SenAlexPadilla
- SenatorWarnock
- ReverendWarnock

Senator handles with `NA` in `senator_handles_table.csv` that belonged to a Senator in `senator_data_match` but hadn't matched correctly and have been manually corrected in
`senator_handles_table.csv`
- senatorhick manually matched to hickenlooper
- sheldonforri manually matched to sheldon whitehouse
- angusformaine manually matched to angus king
- debfornebraska manually matched to deb fischer
- mazieforhawaii manually matched to mazie hirono
- lisaforsenate manually matched to Lisa Murkowski
- votemarsha manually matched to Marsha Blackburn






