---
title: "covariates"
author: "hoskisson"
date: "2023-03-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rtweet)
library(tidyverse)
```

## Compile a table with list of Senators in the 117th congress
Sources:
https://www.congress.gov/members?q=%7B%22congress%22%3A117%2C%22chamber%22%3A%22Senate%22%7D
https://github.com/unitedstates/congress-legislators
```{r}
legislators_current <- read.csv("data/legislators-current.csv") %>%
  filter(type == "sen")
legislators_current$last_name <- tolower(legislators_current$last_name)
legislators_current$first_name <- tolower(legislators_current$first_name)


legislators_historical <- read.csv("data/legislators-historical.csv") %>%
  filter(type == "sen")

legislators_historical$last_name <- tolower(legislators_historical$last_name)
legislators_historical$first_name <- tolower(legislators_historical$first_name)
# data I compiled by hand of the 117th congress
# omitted Kamala Harris and Kelly Loeffler because they were not in chamber
# at time of votes on bills I'm interested in
senator_data <- read.csv("data/senator_data.csv")
```

Join current legislators data
```{r}
# join with current legislators list
senator_data_a <- senator_data %>%
  left_join(legislators_current, by = c("last_name", "first_name")) %>%
  select(c(id:first_name, middle_name, full_name, birthday, gender.y, state.y, type, party.y, govtrack_id, ballotpedia_id))

# clean joined data
senator_data_a <- senator_data_a %>%
  mutate(
    party = party.y,
    gender = gender.y,
    state = state.y
  ) %>%
  select(-party.y, -gender.y, -state.y) %>%
  filter(!is.na(party)) # only keep the ones we have data for--use party column to indicate this
```

Join historical legislator data
```{r}
senator_data_b <- senator_data %>%
  left_join(legislators_historical, by = c("last_name", "first_name")) %>%
  select(c(id:first_name, middle_name, full_name, birthday, gender.y, state.y, type, party.y, govtrack_id, ballotpedia_id))

# clean joined data
senator_data_b <- senator_data_b %>%
  mutate(
    party = party.y,
    gender = gender.y,
    state = state.y
  ) %>%
  select(-party.y, -gender.y, -state.y) %>%
  filter(!is.na(party)) # only keep the ones we have data for--use party column to indicate this

# remove JFK because it is a false match
senator_data_b <- senator_data_b %>%
  filter(last_name != "kennedy")
```

Join current and historical together
```{r}
senator_data_c <- full_join(senator_data_a, senator_data_b) %>%
  arrange(id)
```

record senator_data_c
```{r}
write.csv(senator_data_c,"data/senator_data_c.csv")
```

## Add race and ethnicity

Read in race and ethnicity datasets

*Sources for these:*
Export list of members by biographical characteristics. Washington: CQ Press. Dynamically generated March 31, 2023, from CQ Press Electronic Library, CQ Press Congress Collection: https://library.cqpress.com/congress/export.php?which=memberbioadv&congress2=236&position2=2&yearlimit=0&race=1
Export list of members by biographical characteristics. Washington: CQ Press. Dynamically generated March 31, 2023, from CQ Press Electronic Library, CQ Press Congress Collection: https://library.cqpress.com/congress/export.php?which=memberbioadv&congress2=236&position2=2&yearlimit=0&race=4
Export list of members by biographical characteristics. Washington: CQ Press. Dynamically generated March 31, 2023, from CQ Press Electronic Library, CQ Press Congress Collection: https://library.cqpress.com/congress/export.php?which=memberbioadv&congress2=236&position2=2&yearlimit=0&race=6
Export list of members by biographical characteristics. Washington: CQ Press. Dynamically generated March 31, 2023, from CQ Press Electronic Library, CQ Press Congress Collection: https://library.cqpress.com/congress/export.php?which=memberbioadv&congress2=236&position2=2&yearlimit=0&race=3
Export list of members by biographical characteristics. Washington: CQ Press. Dynamically generated March 31, 2023, from CQ Press Electronic Library, CQ Press Congress Collection: https://library.cqpress.com/congress/export.php?which=memberbioadv&congress2=236&position2=2&yearlimit=0&race=2

Some of the first names have been manually altered to match my previous data. For example, Addison Mitch McConnell was 
changed to Mitch McConnel to match what was in my senator dataset even though Addison Mitch McConnell is probably
the correct name.

Alejandro (Alex) Padilla is latino per: https://history.house.gov/People/Search?Term=Search&SearchIn=LastName&ShowNonMember=true&ShowNonMember=false&Office=&Leadership=&State=&Party=&ContinentalCongress=false&BlackAmericansInCongress=false&WomenInCongress=false&HispanicAmericansInCongress=true&HispanicAmericansInCongress=false&AsianPacificAmericansInCongress=false&CongressNumberList=117&PreviousSearch=Search%2cLastName%2c%2c%2c%2c%2cFalse%2cFalse%2cFalse%2c117%2cLastName&CurrentPage=4&SortOrder=LastName&ResultType=Grid&Command=3

Added Raphel Warnock to African American list per:
https://history.house.gov/People/Search?Term=Search&SearchIn=LastName&ShowNonMember=true&ShowNonMember=false&Office=&Leadership=&State=&Party=&ContinentalCongress=false&BlackAmericansInCongress=true&BlackAmericansInCongress=false&WomenInCongress=false&HispanicAmericansInCongress=false&AsianPacificAmericansInCongress=false&CongressNumberList=117&PreviousSearch=Search%2cLastName%2c%2c%2c%2c%2cFalse%2cTrue%2cFalse%2c117%2cLastName&CurrentPage=1&SortOrder=LastName&ResultType=Grid&Command=6

```{r}
hispanic_senators <- read.csv("data/race_ethnicity/hispanic_117_senate.csv")
race_not_specified_senators <- read.csv("data/race_ethnicity/race_not_specified_117_senate.csv")
white_senators <- read.csv("data/race_ethnicity/white_117_senate.csv")
african_american_senators <- read.csv("data/race_ethnicity/african_american_117_senate.csv")
asian_american_senators <- read.csv("data/race_ethnicity/asian_american_117_senate.csv")
```
```{r}
hispanic_senators <- data.frame(lapply(hispanic_senators, tolower))
race_not_specified_senators <- data.frame(lapply(race_not_specified_senators, tolower))
white_senators <- data.frame(lapply(white_senators, tolower))
african_american_senators <- data.frame(lapply(african_american_senators, tolower))
asian_american_senators <- data.frame(lapply(asian_american_senators, tolower))
```




Add the race data to senator data
```{r}
race_data_senators <- rbind(hispanic_senators, race_not_specified_senators, white_senators, african_american_senators, asian_american_senators)

senator_data_d <- senator_data_c %>%
  left_join(select(race_data_senators, Race, Last, First), by = c("last_name" = "Last", "first_name" = "First"))
```






```{r}
members <- lists_members(list_id = 63915645 )
senator_handles_list <- members$screen_name
senator_handles_df<-as.data.frame(senator_handles_list)
write.csv(senator_handles_df$senator_handles_list, "data/senator_handles.csv")
```



```{r}
rstats <- search_tweets("#rstats", n = 2, include_rts = FALSE)
colnames(rstats)
rstats[1:5, c("created_at", "text", "id_str")]
```

```{r}
lookup_tweets(statuses = c("1500932588436860000"))
lookup_users(c("1499557773687800000"))
get_retweets("1499557773687800000")
tweet_get("1500932588436860000")
```

```{r}
user_info <- lookup_users(tweet_id = "123456789", token = token)
```


```{r}
american_rescue_2021 <- get_timeline(
  user=senator_handles_list,
  since_id = c("1500208536156000000"),
  max_id = c("1500932588436860000")
)

  statuses <- c(
    "567053242429734913",
    "266031293945503744",
    "1500932588436865039"
  )

  ## lookup tweets data for given statuses
  tw <- lookup_tweets(statuses)
  tw
```



